{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2021-10-31 main.tex
commits

	\begin{itemize}
		\item Explain problem of naively extending multivariate linear regression to infinite dimensions
	\end{itemize}
	Considering the population model of scalar-on-function linear regression
	\begin{equation}
     Y =  \int \beta(s)X(s) \,dt \ +\epsilon
    \end{equation}
    it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because there are infinitely many solutions for finding the minimizing argument for $\hat{\beta}$. Define 
    \begin{equation}
  	c_{X}(t,s) = E[X(t)X(s)],\: c_{XY}(t) = E[X(t)Y], 
    \end{equation}
   Under the assumption that $X$ is independent from $\epsilon$ we obtain
   \begin{equation}
     c_{XY}(t) = E[X(t)\int \beta(t)X(s) \,dt \ +\epsilon
   \end{equation}
    \begin{equation}
     c_{XY}(t) = \int \beta(s)\,dt \: E[X(s)X(t)| X] + E[\epsilon |X]
  	\end{equation}
   	\begin{equation}
    	c_{XY}(t) = \int c_{X}(t,s) \beta(s) \,ds 
   \end{equation}

  This results in practice in a large number of equations, which are difficult to solve. Even if solved, this results in a noisy function $\beta(\dot{•})$ that is not useful for interpretation since it does bot utilize the intuition of smooth functions. Another reason why estimation is not feasible using this approach is colinearity. Approximate the scalar-on-functional regression as
  	\begin{equation}
     Y_i = \sum_{i = 1}^{n} \beta(t_{i})X_1(t_{i}) + \epsilon_{i}
    \end{equation}, it becomes obvious that if $t_{i}$ is close to $t_{i'}$, $X_{i}(t_{i})$ is close to $X_{i}(t_{i'})$, so there will be vectors $X_{i}$ thatare stronlgx correlated and thus lead to large variances and not feasible estimation.

>>>>

	\begin{itemize}
		\item Explain problem of naively extending multivariate linear regression to infinite dimensions
	\end{itemize}
	Considering the population model of scalar-on-function linear regression
	\begin{equation}
     Y =  \int \beta(s)X(s) \,dt \ +\epsilon
    \end{equation}
    it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because there are infinitely many solutions for finding the minimizing argument for $\hat{\beta}$. Define 
    \begin{equation}
  	c_{X}(t,s) = E[X(t)X(s)],\: c_{XY}(t) = E[X(t)Y].
    \end{equation}
   Under the assumption that $X$ is independent from $\epsilon$ we obtain
   \begin{equation}
     c_{XY}(t) = E[X(t)\int \beta(s)X(s) \,ds \ +\epsilon]
   \end{equation}
    \begin{equation}
     c_{XY}(t) =  E[\int \beta(s)X(s)X(t)\,ds\:|\: X] + E[\epsilon |X]
  	\end{equation}
   	\begin{equation}
    	c_{XY}(t) = \int c_{X}(t,s) \beta(s) \,ds 
   \end{equation}

  This results in practice in a large number of equations, which are difficult to solve. Even if solved, this results in a noisy function $\beta(\dot{•})$ that is not useful for interpretation since it does bot utilize the intuition of smooth functions. Another reason why estimation is not feasible using this approach is colinearity. Approximate the scalar-on-functional regression as
  	\begin{equation}
     Y_i = \sum_{i = 1}^{n} \beta(t_{i})X_1(t_{i}) + \epsilon_{i}.
    \end{equation}It becomes obvious that if $t_{i}$ is close to $t_{i'}$, $X_{i}(t_{i})$ is close to $X_{i}(t_{i'})$, so there will be vectors $X_{i}$ thatare stronlgx correlated and thus lead to large variances and not feasible estimation.
